\section{Introduction}
Security has become a crucial issue for all modern computing and communication systems.
Network intrusion detection system (NIDS) is the essential protection technology for networked systems.
It automatically monitors a networked system and detect malicious activities or policy violations.
Most current NIDSs adopts that signature based approach, e.g., SNORT~\cite{Snort}, in which
pre-installed rules for specific attacks are used as signature to match known attacks.
The fatal drawback of signature based NIDS is that
it is only effective for previously detected attacks that have an identifiable signature.
As a result, signature database needs to be manually updated whenever a new type of attack
is discovered, with significant effort, by the network administrator.

Therefore, researchers have investigated anomaly detection based approach~\cite{STL-NIDS, LOF, RankingOutliner, NB-Tree, RampLossKSVCR, GAA-ADS},
which overcomes these limitations by adopting data mining or machine learning technique to
model the trustworthy network activities mathematically.
Network traffics that significantly deviate from the built model are treated as malicious.
The advantage of anomaly detection based approach is its ability to detect previously unknown or novel malicious activities.
An on-line model further frees the network administrators from identifying new patterns,
or even new types of the abnormal behaviors in the constantly updating network environment.
However, if the built model for normal or abnormal traffics are not generalized enough,
anomaly based approach will treat unforeseen normal traffic as malicious,
suffering from high false positive.

Deep learning recently catch almost everyone's eye because it achieves significant improvement in image and speech recognition~\cite{AlexNet, SpeechDNN}, natural language processing\cite{Word2Vec}, Go playing~\cite{AlphaGo} and many other domains~\cite{DeepLearning}. 
In this project, we follow the anomaly detection based idea, and tries to enhance it with the
state-of-art machine learning technology, e.g., various deep neural networks trained by innovative algorithms.
We expect these innovative deep learning algorithms and training techniques would directly
help neural networks to achieve better performance in the network intrusion detection problem.
In addition, the unsupervised generative deep learning models are also promising solutions to malicious traffic detection
because they are able to extract useful and hierarchical features from vast amount of unlabeled traffics.
Specifically, we have made the following contributions:
\begin{itemize}
    \item Firstly, we introduce a bundle of deep learning models for the network intrusion detection task,
    including multilayer perceptron, restricted Boltzmann machine, sparse autoencoder, and wide \& deep learning.
    \item We develop and open-source the NetLearner~\cite{NetLearner} to the research community,
    including the implementations of introduced models as well as training procedures,
    both facilitating the reproduction and further extension of this work. 
    \item We conduct a quantitatively comparative study of considered deep learning models with
    two network intrusion detection datasets~\cite{NSL-KDD, UNSW}, measuring accuracy, precision and recall.
\end{itemize}
Preliminary experimental results show that for the NSL-KDD task, 
sparse autoencoder achieves similar performance to the existing machine learning solutions;
deep neural network models with greater generalization capability
achieve better accuracy than SVM for the UNSW-NB15 dataset.